Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-12-06 manuscript/climate_sensitivity_draft.Rmd
minor change

To yield functional understanding of how tree size, microenvironment characteristics, and species' traits collectively shape drought responses, we test a series of hypotheses and associated specific predictions (Table 1) based on the combination of tree-ring records from three droughts (1966, 1977, 1999), species functional and hydraulic trait measurements, and forest census data from a 25.6-ha ForestGEO plot in Virginia (USA). First, we focus on the role of tree size and its interaction with microenvironment. We confirm that, consistent with most forests globally, larger-diameter trees tend to have lower drought resistance in this forest, which is in a region (eastern North America) represented by only two studies in [@bennett_larger_2015] (*H1.0*). 
We then test hypotheses designed to disentangle the relative importance of tree height (*H1.1*), crown exposure (*H1.2*), and soil water availability, which should be greater for larger trees in dry but not in perpetually wet microsites (*H1.3*). 
Second, we focus on the role of species' functional and hydraulic traits and their interaction with tree height. We expect that ring-porous species would have greater drought resistance than semi-ring and diffuse porous species, as has been previously observed [@kannenberg_linking_2019; @elliott_forest_2015; @friedrichs_species-specific_2009]. We test predictions that drought resistance are **negatively** correlated with wood density (following patterns observed by @hoffmann_hydraulic_2011) and positively correlated with specific leaf area, but that hydraulic leaf traits including $PLA_{dry}$ and $\pi_{tlp}$ are better predictors (*H2.1*). 
We then test whether these traits correlate with tree height (*H2.2*), potentially driving the observed tendency for taller trees to suffer more during drought after accounting for trait effects (*H2.3*). 
Finally, we focused on variability among droughts, asking how community resistance varied across droughts (*H3.1*) and whether the factors confirming vulnerability or resistance varied across droughts (*H3.2*).

>>>>

To yield functional understanding of how tree size, microenvironment characteristics, and species' traits collectively shape drought responses, we test a series of hypotheses and associated specific predictions (Table 1) based on the combination of tree-ring records from three droughts (1966, 1977, 1999), species functional and hydraulic trait measurements, and forest census data from a 25.6-ha ForestGEO plot in Virginia (USA). First, we focus on the role of tree size and its interaction with microenvironment. We confirm that, consistent with most forests globally, larger-diameter trees tend to have lower drought resistance in this forest, which is in a region (eastern North America) represented by only two studies in [@bennett_larger_2015] (*H1.0*). 
We then test hypotheses designed to disentangle the relative importance of tree height (*H1.1*), crown exposure (*H1.2*), and soil water availability, which should be greater for larger trees in dry but not in perpetually wet microsites (*H1.3*). 
Second, we focus on the role of species' functional and hydraulic traits and their interaction with tree height. We test predictions that drought resistance is **negatively** correlated with wood density (following patterns observed by @hoffmann_hydraulic_2011) and positively correlated with specific leaf area, but that hydraulic leaf traits including $PLA_{dry}$ and $\pi_{tlp}$ are better predictors (*H2.1*). We expect that ring-porous species would have greater drought resistance than semi-ring and diffuse-porous species, as has been previously observed [@kannenberg_linking_2019; @elliott_forest_2015; @friedrichs_species-specific_2009].  
We then test whether these traits correlate with tree height (*H2.2*), potentially driving the observed tendency for taller trees to suffer more during drought after accounting for trait effects (*H2.3*). 
Finally, we focused on variability among droughts, asking how community resistance varied across droughts (*H3.1*) and whether the factors confirming vulnerability or resistance varied across droughts (*H3.2*).
